\def\thefootnote{}%Remove footnote numbering
\documentclass[12pt,a4paper]{article}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage[sort&compress]{natbib}
\doublespacing
\newif\iflatextortf
\bibstyle{nature}
\addtolength{\topmargin}{-1cm}
\addtolength{\textheight}{3cm}
\addtolength{\oddsidemargin}{-1cm}
\addtolength{\textwidth}{2cm}
\begin{document}
{\noindent\bf This is the title to a fake manuscript}

{\raggedright\noindent Joe Bloggs\textsuperscript{1,*},
Oregano Marjoram\textsuperscript{2}
\vskip 10pt\noindent%
\hfil\break
%
\textsuperscript{1}Naritasan Shinshoji Temple, 1 Narita, Narita City, Chiba
113-0032, Japan
\footnote{%
\textsuperscript{*}Also at:
Royal Botanic Gardens, Kew, Richmond, Surrey TW9 3AB, UK
}
\vskip 5pt\noindent%
%
\textsuperscript{2}Royal Botanic Gardens, Kew, Richmond, Surrey TW9 3AB, UK

\vskip 5pt\noindent%

Manuscript for submission to {\em Nature}: May 12, 2010; revised Oct. 13, 2010.
\vskip 10pt\noindent
\doublespacing }

{\bf 
According to the handbook of van Leunen\citep{Birch1952, Stevenson1981},
this paragraph---and certainly this
section---should be longer than one sentence
\citep{FearnLoper1981}.
According to the handbook of van Leunen, this paragraph---and certainly this
This may have a seismically observable signal.
}

Here we see if the reference\citep{Stevenson1981, Woodetal2006}
to the Narendra article comes out OK, in particular,
with volume, number \& pages.

The necessary information for those who would use BibTeX
is available in the 1988 document of Prof.\ Patashnik\citep{Rubieetal2004,
Ozawaetal2008,
Frostetal2010,
HiltyCrafts1952}.
Interested readers who can read French may also
want to read Poussin's proof\citep{LayYoung1990,
Garneroetal1993,
Tanaka2007,
AlexandrakisEaton2010},
though it has nothing at all to do with BibTeX.

\bigskip\noindent
{\bf Methods summary}.
Data are from the Sacred Place of Bando Fudasho Kannon number 8, to which
believers from far and near visit to pay homage.
This place is dedicated to the Eleven-headed Kanzeon bosatsu.
Designated as Chiba Prefectural Tangible Cultural Asset.

%%\bibliography{bib_style}
\begin{thebibliography}{10}
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\providecommand{\bibinfo}[2]{#2}
\providecommand{\eprint}[2][]{\url{#2}}

\bibitem{Birch1952}
\bibinfo{author}{Birch, F.}
\newblock \bibinfo{title}{{Elasticity and constitution of the Earth's
  interior}}.
\newblock \emph{\bibinfo{journal}{J. Geophys. Res.}}
  \textbf{\bibinfo{volume}{57}}, \bibinfo{pages}{227--286}
  (\bibinfo{year}{1952}).

\bibitem{Stevenson1981}
\bibinfo{author}{Stevenson, D.~J.}
\newblock \bibinfo{title}{{Models of the Earth's core}}.
\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{214}},
  \bibinfo{pages}{611--619} (\bibinfo{year}{1981}).

\bibitem{FearnLoper1981}
\bibinfo{author}{Fearn, D.~R.} \& \bibinfo{author}{Loper, D.~E.}
\newblock \bibinfo{title}{{Compositional convection and stratification of
  Earth's core}}.
\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{289}},
  \bibinfo{pages}{393--394} (\bibinfo{year}{1981}).

\bibitem{Woodetal2006}
\bibinfo{author}{Wood, B.~J.}, \bibinfo{author}{Walter, M.~J.} \&
  \bibinfo{author}{Wade, J.}
\newblock \bibinfo{title}{{Accretion of the Earth and segregation of its
  core}}.
\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{441}},
  \bibinfo{pages}{825--833} (\bibinfo{year}{2006}).

\bibitem{Rubieetal2004}
\bibinfo{author}{Rubie, D.~C.}, \bibinfo{author}{Gessmann, C.~K.} \&
  \bibinfo{author}{Frost, D.~J.}
\newblock \bibinfo{title}{{Partitioning of oxygen during core formation on the
  Earth and Mars}}.
\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{429}},
  \bibinfo{pages}{58--61} (\bibinfo{year}{2004}).

\bibitem{Ozawaetal2008}
\bibinfo{author}{Ozawa, H.} \emph{et~al.}
\newblock \bibinfo{title}{{Chemical equilibrium between ferropericlase and
  molten iron to 134 GPa and implications for iron content at the bottom of the
  mantle}}.
\newblock \emph{\bibinfo{journal}{Geophys. Res. Lett.}}
  \textbf{\bibinfo{volume}{34}}, \bibinfo{pages}{doi:10.1029/2007GL032648}
  (\bibinfo{year}{2008}).

\bibitem{Frostetal2010}
\bibinfo{author}{Frost, D.~J.} \emph{et~al.}
\newblock \bibinfo{title}{{The partitioning of oxygen between the Earth's
  mantle and core}}.
\newblock \emph{\bibinfo{journal}{J. Geophys. Res.}}
  \textbf{\bibinfo{volume}{115}}, \bibinfo{pages}{doi:10.1029/2009JB006302}
  (\bibinfo{year}{2010}).

\bibitem{HiltyCrafts1952}
\bibinfo{author}{Hilty, D.~C.} \& \bibinfo{author}{Crafts, W.}
\newblock \bibinfo{title}{{Liquidus surface of the Fe-S-O system}}.
\newblock \emph{\bibinfo{journal}{J. Metals (Trans. AIME)}}
  \textbf{\bibinfo{volume}{4}}, \bibinfo{pages}{1307--1312}
  (\bibinfo{year}{1952}).

\bibitem{LayYoung1990}
\bibinfo{author}{Lay, T.} \& \bibinfo{author}{Young, C.}
\newblock \bibinfo{title}{{The stably-stratified outermost core revisited}}.
\newblock \emph{\bibinfo{journal}{Geophys. Res. Lett.}}
  \textbf{\bibinfo{volume}{17}}, \bibinfo{pages}{2001--2004}
  (\bibinfo{year}{1990}).

\bibitem{Garneroetal1993}
\bibinfo{author}{Garnero, E.~J.}, \bibinfo{author}{Helmberger, D.~V.} \&
  \bibinfo{author}{Grand, S.~P.}
\newblock \bibinfo{title}{{Constraining outermost core velocity with {S$m$KS}
  waves}}.
\newblock \emph{\bibinfo{journal}{Geophys. Res. Lett.}}
  \textbf{\bibinfo{volume}{20}}, \bibinfo{pages}{2463--2466}
  (\bibinfo{year}{1993}).

\bibitem{Tanaka2007}
\bibinfo{author}{Tanaka, S.}
\newblock \bibinfo{title}{{Possibility of a low P-wave velocity layer in the
  outermost core from global {S$m$KS} waveforms}}.
\newblock \emph{\bibinfo{journal}{Earth Planet. Sci. Lett.}}
  \textbf{\bibinfo{volume}{259}}, \bibinfo{pages}{486--499}
  (\bibinfo{year}{2007}).

\bibitem{AlexandrakisEaton2010}
\bibinfo{author}{Alexandrakis, C.} \& \bibinfo{author}{Eaton, D.~W.}
\newblock \bibinfo{title}{{Precise seismic-wave velocity atop Earth's core: No
  evidence for outer-core stratification}}.
\newblock \emph{\bibinfo{journal}{Phys. Earth Planet. Inter.}}
  \textbf{\bibinfo{volume}{180}}, \bibinfo{pages}{59--65}
  (\bibinfo{year}{2010}).

\bibitem{DziewonskiAnderson1981}
\bibinfo{author}{Dziewonski, A.} \& \bibinfo{author}{Anderson, D.~L.}
\newblock \bibinfo{title}{{Preliminary reference Earth model}}.
\newblock \emph{\bibinfo{journal}{Phys. Earth Planet. Inter.}}
  \textbf{\bibinfo{volume}{25}}, \bibinfo{pages}{297--356}
  (\bibinfo{year}{1981}).

\bibitem{HelffrichKaneshima2004}
\bibinfo{author}{Helffrich, G.} \& \bibinfo{author}{Kaneshima, S.}
\newblock \bibinfo{title}{{Seismological constraints on core composition from
  Fe-O-S liquid immiscibility}}.
\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{306}},
  \bibinfo{pages}{2239--2242} (\bibinfo{year}{2004}).

\bibitem{MastersGubbins2003}
\bibinfo{author}{Masters, G.} \& \bibinfo{author}{Gubbins, D.}
\newblock \bibinfo{title}{{On the resolution of density within the Earth}}.
\newblock \emph{\bibinfo{journal}{Phys. Earth Planet. Inter.}}
  \textbf{\bibinfo{volume}{140}}, \bibinfo{pages}{159--167}
  (\bibinfo{year}{2003}).

\bibitem{Loper2000}
\bibinfo{author}{Loper, D.~E.}
\newblock \bibinfo{title}{{A model of the dynamical structure of the Earth's
  outer core}}.
\newblock \emph{\bibinfo{journal}{Phys. Earth Planet. Inter.}}
  \textbf{\bibinfo{volume}{117}}, \bibinfo{pages}{179--196}
  (\bibinfo{year}{2000}).

\bibitem{Braginsky1993}
\bibinfo{author}{Braginsky, S.~I.}
\newblock \bibinfo{title}{{MAC-Oscillations of the Hidden Ocean of the Core}}.
\newblock \emph{\bibinfo{journal}{J. Geomag. Geoelectr.}}
  \textbf{\bibinfo{volume}{45}}, \bibinfo{pages}{1517--1538}
  (\bibinfo{year}{1993}).

\bibitem{Gubbinsetal1982}
\bibinfo{author}{Gubbins, D.}, \bibinfo{author}{Thomson, C.} \&
  \bibinfo{author}{Whaler, K.}
\newblock \bibinfo{title}{{Stable regions in the earths liquid core}}.
\newblock \emph{\bibinfo{journal}{Geophys. J. R. astron. Soc.}}
  \textbf{\bibinfo{volume}{68}}, \bibinfo{pages}{241--251}
  (\bibinfo{year}{1982}).

\bibitem{ListerBuffett1998}
\bibinfo{author}{Lister, J.~R.} \& \bibinfo{author}{Buffett, B.~A.}
\newblock \bibinfo{title}{{Stratification of the outer core at the core-mantle
  boundary}}.
\newblock \emph{\bibinfo{journal}{Phys. Earth Planet. Inter.}}
  \textbf{\bibinfo{volume}{105}}, \bibinfo{pages}{5--19}
  (\bibinfo{year}{1998}).

\bibitem{RoseBrenan2001}
\bibinfo{author}{Rose, L.~A.} \& \bibinfo{author}{Brenan, J.~M.}
\newblock \bibinfo{title}{{Wetting Properties of Fe-Ni-Co-Cu-O-S Melts against
  Olivine: Implications for Sulfide Melt Mobility}}.
\newblock \emph{\bibinfo{journal}{Econ. Geol.}} \textbf{\bibinfo{volume}{96}},
  \bibinfo{pages}{145--157} (\bibinfo{year}{2001}).

\bibitem{Usselman1975}
\bibinfo{author}{Usselman, T.~M.}
\newblock \bibinfo{title}{{Experimental approach to the state of the core: Part
  I. The liquidus relations of the Fe-rich portion of the Fe-Ni-S system from
  30 to 100 kb}}.
\newblock \emph{\bibinfo{journal}{Am. J. Sci.}} \textbf{\bibinfo{volume}{275}},
  \bibinfo{pages}{278--290} (\bibinfo{year}{1975}).

\bibitem{KilburnWood1997}
\bibinfo{author}{Kilburn, M.~R.} \& \bibinfo{author}{Wood, B.~J.}
\newblock \bibinfo{title}{{Metal-silicate partitioning and the incompatibility
  of S and Si during core formation}}.
\newblock \emph{\bibinfo{journal}{Earth Planet. Sci. Lett.}}
  \textbf{\bibinfo{volume}{152}}, \bibinfo{pages}{139--148}
  (\bibinfo{year}{1997}).

\bibitem{BuffettSeagle2010}
\bibinfo{author}{Buffett, B.~A.} \& \bibinfo{author}{Seagle, C.~T.}
\newblock \bibinfo{title}{{Stratification of the top of the core due to
  chemical interactions with the mantle}}.
\newblock \emph{\bibinfo{journal}{J. Geophys. Res.}}
  \textbf{\bibinfo{volume}{115}}, \bibinfo{pages}{doi:10.1029/2009JB006751}
  (\bibinfo{year}{2010}).

\bibitem{Watsonetal2008}
\bibinfo{author}{Watson, H.~C.}, \bibinfo{author}{Watson, E.~B.} \&
  \bibinfo{author}{Fei, Y.}
\newblock \bibinfo{title}{{Diffusion of Au, Pd, Re, and P in FeNi alloys at
  High Pressure}}.
\newblock \emph{\bibinfo{journal}{Geochim. Cosmochim. Acta}}
  \textbf{\bibinfo{volume}{72}}, \bibinfo{pages}{3550--3561}
  (\bibinfo{year}{2008}).

\bibitem{Garmanyetal1979}
\bibinfo{author}{Garmany, J.}, \bibinfo{author}{Orcutt, J.~A.} \&
  \bibinfo{author}{Parker, R.~L.}
\newblock \bibinfo{title}{{Travel time inversion: a geometrical approach}}.
\newblock \emph{\bibinfo{journal}{J. Geophys. Res.}}
  \textbf{\bibinfo{volume}{84}}, \bibinfo{pages}{3615--3622}
  (\bibinfo{year}{1979}).

\bibitem{Mastersetal2000}
\bibinfo{author}{Masters, G.}, \bibinfo{author}{Laske, G.},
  \bibinfo{author}{Bolton, H.} \& \bibinfo{author}{Dziewonski, A.}
\newblock \bibinfo{title}{{The relative behavior of shear velocity, bulk sound
  speed, and compressional velocity in the mantle: Implications for chemical
  and thermal structure}}.
\newblock In \bibinfo{editor}{Karato, S.-I.}, \bibinfo{editor}{Forte, A.~M.},
  \bibinfo{editor}{Liebermann, R.~C.}, \bibinfo{editor}{Masters, G.} \&
  \bibinfo{editor}{Stixrude, L.} (eds.) \emph{\bibinfo{booktitle}{{Earth's deep
  interior: Mineral physics and tomography from the atomic to the global
  scale}}}, vol. \bibinfo{volume}{117} of \emph{\bibinfo{series}{{Geophys.
  Mon.}}}, \bibinfo{pages}{63--87} (\bibinfo{publisher}{{Amer. Geophys. Un.}},
  \bibinfo{year}{2000}).

\bibitem{KennettEngdahl1991}
\bibinfo{author}{Kennett, B. L.~N.} \& \bibinfo{author}{Engdahl, E.~R.}
\newblock \bibinfo{title}{{Traveltimes for global earthquake location and phase
  identification}}.
\newblock \emph{\bibinfo{journal}{Geophys. J. Int.}}
  \textbf{\bibinfo{volume}{105}}, \bibinfo{pages}{429--465}
  (\bibinfo{year}{1991}).

\bibitem{MorelliDziewonski1993}
\bibinfo{author}{Morelli, A.} \& \bibinfo{author}{Dziewonski, A.~M.}
\newblock \bibinfo{title}{{Body wave traveltimes and a spherically symmetric P-
  and S-wave velocity model}}.
\newblock \emph{\bibinfo{journal}{Geophys. J. Int.}}
  \textbf{\bibinfo{volume}{112}}, \bibinfo{pages}{178--194}
  (\bibinfo{year}{1993}).

\bibitem{Kennettetal1995}
\bibinfo{author}{Kennett, B. L.~N.}, \bibinfo{author}{Engdahl, E.~R.} \&
  \bibinfo{author}{Buland, R.}
\newblock \bibinfo{title}{{Constraints on seismic velocities in the Earth from
  traveltimes}}.
\newblock \emph{\bibinfo{journal}{Geophys. J. Int.}}
  \textbf{\bibinfo{volume}{126}}, \bibinfo{pages}{108--124}
  (\bibinfo{year}{1995}).

\bibitem{Alfeetal2002}
\bibinfo{author}{Alf\'{e}}, \bibinfo{author}{Price, G.~D.} \&
  \bibinfo{author}{Gillan, M.~J.}
\newblock \bibinfo{title}{{Iron under Earth's core conditions: Liquid-state
  thermodynamics and high-pressure melting curve from ab initio calculations}}.
\newblock \emph{\bibinfo{journal}{Phys. Rev. B}} \textbf{\bibinfo{volume}{65}},
  \bibinfo{pages}{art. no. 165118} (\bibinfo{year}{2002}).

\end{thebibliography}

\bigskip\noindent
{\bf Acknowledgements}.
This work was supported by air travel from Flying Carpet Airlines.

\bigskip\noindent
{\bf Author Contributions}.
Authors contributed equally to the project.

\bigskip\noindent
{\bf Competing Interests}.
The authors declare no competing financial interests.

\bigskip\noindent
Figure 1.
Experiment geometry.
\hfil\break

\bigskip\noindent
Figure 2.
Data and velocity profile.

\bigskip\noindent
Figure 3.
Compositional profile.

\section*{Methods.}
\renewcommand{\thefigure}{S\arabic{figure}}
\setcounter{figure}{0}
\renewcommand{\thetable}{ST\arabic{table}}
\renewcommand{\tablename}{}
\setcounter{table}{0}
\section*{Analysis}

The web page http://www.cs.stir.ac.uk/~kjt/software/latex/showbst.html also
illustrates several bibliography styles for easy comparison.
Of the 44 styles listed above, the first 21 insert just a number in brackets at
the point of citation [2], while items 22-37 use some variation of author/year
[K.S.Narenda and K.Parthsarathy, 1990], and the rest use some idiosyncratic
reference code
\citep{EatonKendall2006,
Kind1979}
Some of the styles re-order the references in the bibliography in alphabetical
order of author, while others list them in the order that they are first cited.
Several of these styles are part of all LaTeX installations, and others can be
downloaded from http://www.tug.org/tex-archive/biblio/bibtex/contrib/.
Each is a file with the suffix .bst; for example, to use abbrvnat style, you
must have the file abbrvnat.bst installed in your LaTeX directory, or in your
current working directory, or anywhere where LaTeX can find it.

Those dissatisfied with the 100+ styles available online can design their own,
if they wish; see Oren Patashnik's Designing BibTeX Styles
\citep{Andersonetal1993}.

%%\bibliography{bib_style}
\begin{thebibliography}{10}
\setcounter{NAT@ctr}{30}
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\iflatextortf \relax
\else
\providecommand{\bibinfo}[2]{#2}
\providecommand{\eprint}[2][]{\url{#2}}
\fi

\bibitem{Kind1979}
\bibinfo{author}{Kind, R.}
\newblock \bibinfo{title}{{Extensions of the reflectivity method for a buried
  source}}.
\newblock \emph{\bibinfo{journal}{J. Geophys.}} \textbf{\bibinfo{volume}{45}},
  \bibinfo{pages}{373--380} (\bibinfo{year}{1979}).

\bibitem{EatonKendall2006}
\bibinfo{author}{Eaton, D.~W.} \& \bibinfo{author}{Kendall, J.-M.}
\newblock \bibinfo{title}{{Improving seismic resolution of outermost core
  structure by multichannel analysis and deconvolution of broadband SmKS
  phases}}.
\newblock \emph{\bibinfo{journal}{Phys. Earth Planet. Inter.}}
  \textbf{\bibinfo{volume}{155}}, \bibinfo{pages}{104--119}
  (\bibinfo{year}{2006}).

\bibitem{Boehler1992}
\bibinfo{author}{Boehler, R.}
\newblock \bibinfo{title}{{Melting of the Fe-FeO and the Fe-FeS systems at
  high-pressure - constraints on core temperatures}}.
\newblock \emph{\bibinfo{journal}{Earth Planet. Sci. Lett.}}
  \textbf{\bibinfo{volume}{111}}, \bibinfo{pages}{217--227}
  (\bibinfo{year}{1992}).

\bibitem{Boehler1993}
\bibinfo{author}{Boehler, R.}
\newblock \bibinfo{title}{{Temperatures in the earths core from melting-point
  measurements of iron at high static pressures}}.
\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{363}},
  \bibinfo{pages}{534--536} (\bibinfo{year}{1993}).

\bibitem{Svendsenetal1989}
\bibinfo{author}{Svendsen, B.}, \bibinfo{author}{Anderson, W.~W.},
  \bibinfo{author}{Ahrens, T.~J.} \& \bibinfo{author}{Bass, J.~D.}
\newblock \bibinfo{title}{{Ideal Fe-FeS, Fe-FeO phase relations and Earth's
  core}}.
\newblock \emph{\bibinfo{journal}{Phys. Earth Planet. Inter.}}
  \textbf{\bibinfo{volume}{55}}, \bibinfo{pages}{154--186}
  (\bibinfo{year}{1989}).

\bibitem{Feietal1990}
\bibinfo{author}{Fei, Y.}, \bibinfo{author}{Saxena, S.~K.} \&
  \bibinfo{author}{Navrotsky, A.}
\newblock \bibinfo{title}{{Internally Consistent Thermodynamic Data and
  Equilibrium Phase Relations for Compounds in the System MgO-SiO2 at High
  Pressure and high temperature}}.
\newblock \emph{\bibinfo{journal}{J. Geophys. Res.}}
  \textbf{\bibinfo{volume}{95}}, \bibinfo{pages}{6915--6928}
  (\bibinfo{year}{1990}).

\bibitem{Andersonetal1992}
\bibinfo{author}{Anderson, O.~L.}, \bibinfo{author}{Isaak, D.} \&
  \bibinfo{author}{Oda, H.}
\newblock \bibinfo{title}{{High-temperature elastic constant data on minerals
  relevant to geophysics}}.
\newblock \emph{\bibinfo{journal}{Rev. Geophys.}}
  \textbf{\bibinfo{volume}{30}}, \bibinfo{pages}{57--90}
  (\bibinfo{year}{1992}).

\bibitem{BinaHelffrich1992}
\bibinfo{author}{Bina, C.~R.} \& \bibinfo{author}{Helffrich, G.}
\newblock \bibinfo{title}{{Calculation of elastic properties from thermodynamic
  equation of state principles}}.
\newblock \emph{\bibinfo{journal}{Annu. Rev. Earth Planet. Sci.}}
  \textbf{\bibinfo{volume}{20}}, \bibinfo{pages}{527--552}
  (\bibinfo{year}{1992}).

\bibitem{Morardetal2007}
\bibinfo{author}{Morard, G.} \emph{et~al.}
\newblock \bibinfo{title}{{Structure of eutectic Fe-FeS melts to pressures up
  to 17 GPa: Implications for planetary cores}}.
\newblock \emph{\bibinfo{journal}{Earth Planet. Sci. Lett.}}
  \textbf{\bibinfo{volume}{263}}, \bibinfo{pages}{128--139}
  (\bibinfo{year}{2007}).

\bibitem{Andersonetal1993}
\bibinfo{author}{Anderson, O.~L.}, \bibinfo{author}{Oda, H.},
  \bibinfo{author}{Chopelas, A.} \& \bibinfo{author}{Isaak, D.}
\newblock \bibinfo{title}{{A Thermodynamic Theory of the Gr\"{u}neisen Ratio at
  Extreme Conditions: MgO as an Example}}.
\newblock \emph{\bibinfo{journal}{Phys. Chem. Minerals}}
  \textbf{\bibinfo{volume}{19}}, \bibinfo{pages}{369--380}
  (\bibinfo{year}{1993}).

\end{thebibliography}
\end{document}
