\subsection{This is the first subsection in file \texttt{include2.tex}}\label{section21}Here is some text to create a paragraph or two so that wecan see if this works or not.  It will be interesting to seeif the labels work properly.  As I create these testing filesI realize that I need to add parsing support for \verb#\input#and \verb#\include# in the getSection function.   Furthermore,after reading the \LaTeX{} book, I see that \verb#\include# files will all start on a new page.  This is not the case for\verb#\input# files.  Here is a reference to the next subsection \ref{section22}.\subsection{This is the second subsection in file \texttt{include2.tex}}\label{section22}Here is some text to create a paragraph or two so that wecan see if this works or not.  It will be interesting to seeif the labels work properly.  As I create these testing filesI realize that I need to add parsing support for \verb#\input#and \verb#\include# in the getSection function.   Furthermore,after reading the \LaTeX{} book, I see that \verb#\include# files will all start on a new page.  This is not the case for\verb#\input# files.  Here is a reference to the previous subsection \ref{section21}.Here is a reference to the first section in \texttt{include1.tex}\ref{section11}.Now we include another file from within an included file\section{Testing how including files within other files}\label{section3}The trick here is to test the various ways that files might be includedwithin another file.  \input{include3}This is the content following \verb#\input{include3}#.  There should be nopagebreak.\input include4This is the content following \verb#\input include4 #.  There should be nopagebreak.